Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-08-17 manuscript.Rmd
Small updates manuscript

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : " "
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika Stefan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia Haaf"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "University of Amsterdam"

@@

We do not have ownership of the data used in this study, but the the data set is publicly available on [GitHub](https://github.com/PerceptionCognitionLab/data0/blob/master/lexDec-dist5/). The `.stan` models, results of the model fit, and model comparison are available on [our GitHub repository]().

@@

The R code used for the analyses and figures in this manuscript, and `R` tutorials on BHMs are available under an CC-BY-4.0 license on [our GitHub repository]().

@@

M.V. participated in the design and coordination of this study, performed statistical analyses, and drafted the paper; A.S. participated in the design and coordination of this study, helped with the statistical analyses, interpretation of the results and writing the paper; J.H. (principal investigator) conceived the study, participated in the design and coordination of the study, helped with the statistical analyses, interpretation of results and writing the paper. All authors read and approved the final paper.

>>>>

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "2"
    corresponding : yes    # Define only one corresponding author
    address       : "Wassenaarseweg 52, Leiden"
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika Stefan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia Haaf"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "University of Amsterdam"
  - id            : "2"
    institution   : "Leiden University"

@@

We do not have ownership of the data used in this study, but the the data set is publicly available on [GitHub](https://github.com/PerceptionCognitionLab/data0/blob/master/lexDec-dist5/). The `.stan` models, results of the model fit, and model comparison are available on [our GitHub repository](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).

@@

The R code used for the analyses and figures in this manuscript, and `R` tutorials on BHMs are available on [our GitHub repository](https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment).

@@

M.V. participated in the design and coordination of this study, performed statistical analyses, and drafted the paper; A.M.S. participated in the design and coordination of this study, helped with the statistical analyses, interpretation of the results and writing the paper; J.M.H. (principal investigator) conceived the study, participated in the design and coordination of the study, helped with the statistical analyses, interpretation of results and writing the paper. All authors read and approved the final paper.

### 2022-08-17 manuscript.tex
Small updates manuscript

  pdfauthor={Myrthe Veenman1, Angelika Stefan1, \& Julia Haaf1},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{1}, Angelika Stefan\textsuperscript{1}, \& Julia Haaf\textsuperscript{1}}
\date{}

@@

Correspondence concerning this article should be addressed to Myrthe Veenman, . E-mail: \href{mailto:myrthe.veenman@gmail.com}{\nolinkurl{myrthe.veenman@gmail.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Amsterdam}

@@

We do not have ownership of the data used in this study, but the the data set is publicly available on \href{https://github.com/PerceptionCognitionLab/data0/blob/master/lexDec-dist5/}{GitHub}. The \texttt{.stan} models, results of the model fit, and model comparison are available on \href{}{our GitHub repository}.

@@

The R code used for the analyses and figures in this manuscript, and \texttt{R} tutorials on BHMs are available under an CC-BY-4.0 license on \href{}{our GitHub repository}.

>>>>

  pdfauthor={Myrthe Veenman2, Angelika Stefan1, \& Julia Haaf1},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{2}, Angelika Stefan\textsuperscript{1}, \& Julia Haaf\textsuperscript{1}}
\date{}

@@

Correspondence concerning this article should be addressed to Myrthe Veenman, Wassenaarseweg 52, Leiden. E-mail: \href{mailto:myrthe.veenman@gmail.com}{\nolinkurl{myrthe.veenman@gmail.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Amsterdam\\\textsuperscript{2} Leiden University}

@@

We do not have ownership of the data used in this study, but the the data set is publicly available on \href{https://github.com/PerceptionCognitionLab/data0/blob/master/lexDec-dist5/}{GitHub}. The \texttt{.stan} models, results of the model fit, and model comparison are available on \href{https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment}{our GitHub repository}.

@@

The R code used for the analyses and figures in this manuscript, and \texttt{R} tutorials on BHMs are available on \href{https://github.com/MyrtheV/Bayesian-Hierarchical-Modelling-An-Introduction-and-Reassessment}{our GitHub repository}.
